\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
The pseudocode doesn't need to be fucking python

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for inserting beta nodes},
                   label={lst:add_betas}]
def addBetaNodesToFunc(cfg):
  for b in cfg.basic_blocks():
    if b.numPredecessors() == 1 and isBranch(b.pred(0).lastInstruction()):
      test = b.pred(0).lastInstruction()
      # find whether we are the true or false branch
      direction = (b == test.trueTarget())
      if test.op() in RELOPs:
          r = computeRange(test.op(), c, direction)
          x_prime = b.insertFront(Beta(x, r))
          replaceDominatedUses(x, x_prime)

>>>>

\begin{lstlisting}[language=Python,
                   caption={Pseudocode algorithm for inserting beta nodes},
                   label={lst:add_betas}]
def addBetaNodesToFunc(cfg):
  for b in cfg.basic_blocks():
    if b.numPredecessors() == 1 and isBranch(b.pred(0).lastInstruction()):
      test = b.pred(0).lastInstruction()
      # find whether we are the true or false branch
      direction = (b == test.trueTarget())
      if test matches ``x RELOP c'':
          r = computeRange(RELOP, c, direction)
          x_prime = b.insertFront(Beta(x, r))
          replaceDominatedUses(x, x_prime)
